### 2020-03-21 korea.tex
update

Since its appearance in December 2019, the novel coronavirus disease (COVID-19) has spread internationally, including to South Korea.
The first COVID-19 case in South Korea was confirmed on January 20, 2020, from a traveling resident of Wuhan, China.
The epidemic took off in mid-February when COVID-19 began to spread within a church from a city of Daegu --- as of March 18, 2020, 8,413 cases have been confirmed, of which 60\% are linked to the church.
Despite the lack of draconian measures such as in China, the epidemic has been subsiding in South Korea.
Its success in controlling the spread has been widely attributed to its intensive testing.
Here, we describe potential roles of social distancing in mitigating the spread of COVID-19 by comparing epidemics in two geographically separated major cities in South Korea.

@@

We analyze epidemiological data, collected bewteen January 20--March 16, 2020, describing the COVID-19 outbreak in Korea.
Daily number of reported cases in each geographic region was transcribed from press releases by \cite{kcdc}.
Partial line lists were transcribed from press releases and reports from KCDC and various local and provincial government websites.
All data, sources, and original reports are stored in a publicly available GitHub repoository: \url{https://github.com/parksw3/COVID19-Korea}.

@@

We compare epidemiological dynamics of COVID-19 from two cities in which the biggest number of COVID-19 cases have been reported: Daegu and Seoul.
% population size: 2.4 and 9.7 million \citep{kosis}.
Bewteen January 20--March 16, 2020, 6,083 cases were reported from Daegu and 248 from Seoul.
Unlike the epidemic in Daegu, which is characterized by a single, large peak followed by a persistent decrease, the epidemic in Seoul consists of several small outbreaks (\fref{data}).

>>>>

Since its first appearance in Wuhan, China, in December 2019, the novel coronavirus disease (COVID-19) has spread internationally, including to South Korea.
The first COVID-19 case in South Korea was confirmed on January 20, 2020, from a traveling resident of Wuhan, China.
The epidemic then took off in mid-February when COVID-19 began to spread within a church from a city of Daegu --- as of March 18, 2020, 8,413 cases have been confirmed, of which 60\% are linked to the church.
While its success in controlling the epidemic has been widely attributed to its intensive testing, other factors also played a role. 
Here, we describe potential roles of social distancing in mitigating the spread of COVID-19 by comparing epidemics in two geographically separated major cities in South Korea.

@@

We analyze epidemiological data, collected bewteen January 20--March 16, 2020, describing the COVID-19 outbreak in Korea.
Daily number of reported cases in each geographic region was transcribed from press releases by \cite{kcdc}.
Partial line lists were transcribed from press releases and reports from KCDC and various local and provincial government websites.
All data and original reports are stored in a publicly available GitHub repoository: \url{https://github.com/parksw3/COVID19-Korea}.

@@

We compare epidemiological dynamics of COVID-19 from two cities in which the biggest number of COVID-19 cases have been reported: Daegu and Seoul.
Bewteen January 20--March 16, 2020, 6,083 cases were reported from Daegu and 248 from Seoul.
Unlike the epidemic in Daegu, which is characterized by a single, large peak followed by a persistent decrease, the epidemic in Seoul consists of several small outbreaks (\fref{data}).
